Crossing Origins by Crossing Formats

### 2013-02-20 main.tex
Updates in Evaluation and Mitigation

\subsection{Syntax injection}

As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be communicated back to the attacker, or be leveraged in further attacks.

@@

\subsubsection{Readers}

Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
due to its standing as the most commonly used reader. To give a comparison, the 
Google Chrome built-in PDF reader, was selected as it is the default reader to 
user of the browser.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences.

@@

\paragraph{Google Chrome}
Google's browser, Chrome, has built-in support for displaying PDF documents. 
The built-in PDF reader is used by default by the browser, unless it has been 
explicitly disabled by the user. Certain complex PDF documents can not be 
handled by the built-in reader. The built-in reader will then prompt the user 
to open the document in Adobe Reader. As previously noted, the built-in reader 
is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
Reader plug-in is used to render the document.

%\subsection{Bypassing content filters}

@@

\subsection{Alexa top 100}
We have conducted a
study to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
It does not involve polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.

The study is based on supplying the websites with small benign samples 
of PDF syntax, containing keywords and tokens, and examining the responses 
for said tokens. The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format, which have the potential of compromising the 
confidentiality and integrity of the website's users.
%
We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.

@@

%1-2 pages 
\section{Mitigation}
\label{sec:mit}
This section will describe our recommendations for mitigation in each of the
affected components.

@@

To prevent PDF syntax injection attack, the task is simpler. As mentioned in 
Section~\ref{sec:vuln}, there is a limited set of characters that are essential 
to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
user input to remove or encode these characters effectively mitigates the 
vulnerability.

>>>>

\subsection{Syntax injection}
\label{sec:pdf-injection}
As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be communicated back to the attacker, or be leveraged in further attacks.

@@

\subsubsection{Readers}
\label{sec:readers}
Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
due to its standing as the most commonly used reader. To give a comparison, the 
Google Chrome built-in PDF reader, was selected as it is the default reader to 
user of the browser.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.

@@

\paragraph{Google Chrome}
Google's browser, Chrome, has built-in support for displaying PDF documents. 
The built-in PDF reader is used by default by the browser, unless it has been 
explicitly disabled by the user. Certain complex PDF documents can not be 
handled by the built-in reader. The built-in reader will then prompt the user 
to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
Reader plug-in is used to render the document.

\begin{table}[h!]
\begin{tabular}{l||c|c|c}
& object & embed & Adobe is default \\ \hline
Firefox & X & X & X \\ \hline
Chrome & X & X & --- \\ \hline
Safari & X & X & X \\ \hline
Opera & X & X & X \\ \hline
Internet Explorer & --- & X & X %\\ \hline
\end{tabular}
\caption{Comparison of browsers}
\label{tab:comparison}
\end{table}
%\subsection{Bypassing content filters}

@@

\subsection{Alexa top 100}
We have conducted a
study to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
It does not involve polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual websites to prevent exploitation 
before the issues have been properly dealt with. Neither do we want to disclose 
these websites as particularly vulnerable.

The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
were tested, which suggests that more websites are likely vulnerable in input that do
requires authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable;three were susceptible to traditional 
XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that prevented exploitation.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%
We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.

@@

%1-2 pages 
\section{Mitigation}
\label{sec:mit}
This section gives advice on various mitigation approaches available for each of the
affected components, from server to client.

@@

To prevent PDF-based syntax injection attack, the task is simpler. The token-set identified in 
Section~\ref{sec:pdf-injection}, are essential 
to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
user input to remove or encode these characters effectively mitigates the 
vulnerability.
